---
title: "Baseline Commission QA Summary"
author: "Transforming Government Services"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: kable
    highlight: pygment
    number_sections: no
    theme: cerulean
    toc: yes
    toc_collapsed: yes
    toc_depth: 5
    toc_float: yes # Must be after toc_depth
---


```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load in R variables and clarify location ahead of attempting to load
load("my_data.RData")
library(DT)
```

# Background
This HTML document is designed to be the counterpart to the R collation process,
flagging (as far as possible) the completeness of various sections of the baseline 
template commission.

# Services included
The following services baseline data has been collated across `r nrow(sheets_list)` 
input template files.

# Section Completeness
The table below shows how complete each section is across all baseline templates. 
A RAG colour has been assigned with the following thresholds

* White: More than 80% of the fields in a section across all services are complete.
* Yellow: Between 50% and 80% of the fields in a section across all services are complete.
* Red: Less than 50% of the fields in a section are complete.

Please note, these are rough proportions given the varying size of the 
sections themselves. For example, the service objectives table only has 4 
fields. In addition, additional info/free text fields have been separated from 
value fields to provide a more granular overview of key sections of interest.

Where a section is left at the discretion of the service to fill in (i.e.
service\-specific pain points), the proportion of services providing AT LEAST the
first KPI name/Theme has been used but not the overall completion of all fields 
in the relevant table (see 'Field Completion - Optional Sections').

```{r overall, echo = FALSE, warning=FALSE}
datatable(overall_completeness, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          ) %>% 
  formatStyle(1, 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

# Per Service Completion {.tabset}

Please use the tabs to view the section of interest and the proportion of 
fields across all services that have an entry present. 

Please note that the completion of service\-specific KPIs and 
service\-specific challenges can vary wildly across templates in their completion. These figures 
should consequently be taken with a pinch of salt.

```{r service_completion, echo = FALSE, warning=FALSE}
datatable(service_completeness, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") ), 
          rownames = FALSE
          ) %>% 
  formatStyle(c(2:9), 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```
# Field Completion By Section {.tabset}

## Context
```{r context_fields, echo = FALSE, warning=FALSE}
datatable(cntxt_section, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          )  %>% 
  formatStyle(1, 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

## Objectives
```{r objectives_fields, echo = FALSE, warning=FALSE}
datatable(objctvs_section, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          )  %>% 
  formatStyle(1, 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

## CDDO KPIs

### Value Fields
```{r CDDOKPI_fields, echo = FALSE, warning=FALSE}
datatable(cddo_section_KPIs, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          )  %>% 
  formatStyle(1, 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

### Additional Information
```{r CDDOAddInfo_fields, echo = FALSE, warning=FALSE}
datatable(cddo_section_AddInfo, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          )  %>% 
  formatStyle(1, 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

### Free text
```{r CDDOFreeText_fields, echo = FALSE, warning=FALSE}
datatable(cddo_section_FreeText, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          )  %>% 
  formatStyle(1, 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

## CDDO pain points

### Value Fields
```{r CDDOPP_fields, echo = FALSE, warning=FALSE}
datatable(cddoPP_section, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          ) %>% 
  formatStyle(1, 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

### Improvements
```{r CDDOImprovements_fields, echo = FALSE, warning=FALSE}
datatable(cddoPP_section_ImprovementsText, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          ) %>% 
  formatStyle(1, 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

### Challenges 
```{r CDDOChallenges_fields, echo = FALSE, warning=FALSE}
datatable(cddoPP_section_ChallengesText, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          ) %>% 
  formatStyle(1, 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

# Field Completion - Optional Sections {.tabset}

The completion of these fields will vary significantly across services. This table is 
designed to show the proportion of all services that are providing data in these optional fields,
separate from the fields we expect to be filled in. 

## Service-specific KPIs
```{r servspec_KPIs, echo = FALSE, warning=FALSE}
datatable(servspec_section, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          )  %>% 
  formatStyle(c(1:5), 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```

## Service-specific pain points
```{r servspec_PP, echo = FALSE, warning=FALSE}
datatable(servspecPP_section, style = 'bootstrap', options = list(   
            initComplete = JS("function(settings, json) {",  
                              "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",     "}") )
          )  %>% 
  formatStyle(c(1:3), 
    backgroundColor = styleInterval(c(50, 80), c("#ce2029", "#FF08D", "white"))
    , color = styleInterval(c(50, 80), c("white", "black", "black"))
    )
```
